The Sub-Millimetre User Reduction Facility: an iterative map-maker for SCUBA-2

### 2010-11-17 smurf_paper.tex
A few more notes and references

Styles of map-making: maximum likelihood
\citep[e.g.,][]{patanchon2008}; iterative -- see \citet{johnstone2000}
implementation of \citet{wright1996} to remove chop,
\citet{kovacs2008} for SHARC-2 etc.; de-correlation using PCA
analysis \citep[e.g.][]{laurent2005,scott2008}.

@@

@@

\subsection{Data cleaning}
We basically need to correct steps and apply the flatfield correction.

@@

%------------------------------------------------------------------------------
\section{Examples}
\label{sec:data}
%------------------------------------------------------------------------------

>>>>

Styles of map-making: maximum likelihood
\citep[e.g.,][]{patanchon2008}; iterative -- see \citet{johnstone2000}
implementation of \citet{wright1996} to remove chop,
\citet{kovacs2008} for SHARC-2 etc.; de-correlation using PCA
analysis \citep[e.g.][]{laurent2005,scott2008,aguirre2010}.

@@

Show some time series.

Show power spectra.

Show cross-spectra to emphasize how correlated things are?

@@

We express the signal observed by the $i$th bolometer as a function of time,
\begin{equation}
B_i(t) = E(t)[ A(t) + N(t) ] + C(t)
\end{equation}
where $A(t)$ is the time-varying astronomical signal produced by
scanning the telescope across sources, $C(t)$ is a common signal
observed by all of the detectors, $E(t)$ is the time-varying
extinction, which is a function of the telescope elevation and
observing conditions, and $N(t)$ represents all other noise terms. The
common-mode, $C(t)$ has a strong

\subsection{Data cleaning}

\subsubsection{Step correction}

\subsubsection{Flatfields using heater ramps}

\subsubsection{Flatfields using the common-mode signal}

@@

%------------------------------------------------------------------------------
\section{Examples}
\label{sec:examples}
%------------------------------------------------------------------------------
